Ecuador plant species GBIF

### 2023-01-22 code/L0/L0_Ecuador_plants_GBIF.Rmd
update download number

```{r}
occ_download(
pred("taxonKey", 6), 
pred("hasGeospatialIssue", FALSE),
pred("hasCoordinate", TRUE),
pred("country","EC"),
pred("occurrenceStatus","PRESENT"), 
pred_not(pred_in("basisOfRecord",c("FOSSIL_SPECIMEN","LIVING_SPECIMEN"))),
format = "SIMPLE_CSV"
)
```
# Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0065583-220831081235567", path = output_path) %>%
  occ_download_import()
```

@@

```{r}
#using bdvis package
d <- format_bdvis(d, , Latitude = "Latitude", Longitude = "Longitude", Date_collected = "Date_collected", Scientific_name = "scientificName")
bdsummary(d)
d$Date_collected <- as.Date(d$Date_collected)
bdcalendarheat(d)
chronohorogram(d)
getcellid(d, gridscale = 10)
distrigraph(d, ptype = "species")
distrigraph(d, ptype = "efforts")
distrigraph(d, ptype = "cell")
distrigraph(d, ptype = "effortspecies")
tempolar(d, timescale = "m")
bdcomplete(d)
mapgrid(d, ptype = "species", region = "Ecuador")
```

>>>>

```{r}
occ_download(
pred("taxonKey", 6), 
pred("hasGeospatialIssue", FALSE),
pred("hasCoordinate", TRUE),
pred("country","EC"),
pred("occurrenceStatus","PRESENT"), 
pred_not(pred_in("basisOfRecord",c("FOSSIL_SPECIMEN","LIVING_SPECIMEN"))),
format = "SIMPLE_CSV"
)
```
# Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0253091-220831081235567", path = output_path) %>%
  occ_download_import()
```

@@

```{r}
#using bdvis package
d <- format_bdvis(d, , Latitude = "decimalLatitude", Longitude = "decimalLongitude", Date_collected = "eventDate", Scientific_name = "scientificName", Family = "family", Genus = "genus")
```

```{r}
bdsummary(d)
d$Date_collected <- as.Date(d$Date_collected)
bdcalendarheat(d)
getcellid(d, gridscale = 10)
distrigraph(d, ptype = "species")
distrigraph(d, ptype = "efforts")
distrigraph(d, ptype = "cell")
distrigraph(d, ptype = "effortspecies")
bdcomplete(d)
mapgrid(d, ptype = "species", region = "Ecuador")
```
